Mechanising Hylomorphisms for Extraction of Executable Code

### 2025-03-18 paper/lensbans.tex

\newcommand{\lbanana}{%
  \mathopen{\tikz[baseline=0.25em,xscale=0.006em,yscale=0.006em]
  \draw[join=round] (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;\mspace{1mu}}}
\newcommand{\rbanana}{%
  \mathclose{\mspace{1mu}\tikz[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
  \draw[join=round] (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;}}
% filled versions
\newcommand{\Lbanana}{%
  \mathopen{\mspace{1mu}\tikz[baseline=0.25em,xscale=0.006em,yscale=0.006em]
  \fill (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;\mspace{1mu}}}
\newcommand{\Rbanana}{%
  \mathclose{\mspace{1mu}\tikz[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
  \fill (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;}}
% % lens brackets (using TikZ)
% \newcommand{\llens}{%
%   \mathopen{\tikz[baseline=0.25em,xscale=0.006em,yscale=0.006em]
%   \draw[join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
%         to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;\mspace{1mu}}}
% \newcommand{\rlens}{%
%   \mathclose{\mspace{1mu}\tikz[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
%   \draw[join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
%         to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;}}
% filled versions
\newcommand{\Llens}{%
  \mathopen{\tikz[baseline=0.25em,xscale=0.006em,yscale=0.006em]
  \fill (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
        to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;\mspace{1mu}}}
\newcommand{\Rlens}{%
  \mathclose{\mspace{1mu}\tikz[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
  \fill (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
        to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;}}

>>>>

% filled versions
\newcommand{\Lbanana}{%
  \mathopen{\mspace{1mu}\tikz[baseline=0.25em,xscale=0.006em,yscale=0.006em]
  \fill (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;\mspace{1mu}}}
\newcommand{\Rbanana}{%
  \mathclose{\mspace{1mu}\tikz[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
  \fill (2,0) to[out=140,in=-90] (0,3) to[out=90,in=-140] (2,6) -- (2.1,5.9)
              to[out=-120,in=90] (1.2,3) to[out=-90,in=120] (2.1,0.1) -- cycle;}}
% % lens brackets (using TikZ)
% \newcommand{\llens}{%
%   \mathopen{\tikz[baseline=0.25em,xscale=0.006em,yscale=0.006em]
%   \draw[join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
%         to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;\mspace{1mu}}}
% \newcommand{\rlens}{%
%   \mathclose{\mspace{1mu}\tikz[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
%   \draw[join=round] (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
%         to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;}}
% filled versions
\newcommand{\Llens}{%
  \mathopen{\tikz[baseline=0.25em,xscale=0.006em,yscale=0.006em]
  \fill (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
        to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;\mspace{1mu}}}
\newcommand{\Rlens}{%
  \mathclose{\mspace{1mu}\tikz[baseline=0.25em,xscale=-0.006em,yscale=0.006em]
  \fill (1.4,0) -- (0,0) -- (0,6) -- (1.4,6) -- (1.5,5.9)
        to[out=-120,in=90] (0.7,3) to[out=-90,in=120] (1.5,0.1) -- cycle;}}
